\heading{Experience \& Achievements}

\vspace{-1.2em}

\begin{longtable}{L!{\sep}R}
  \rctline{Mar 2017}{
    Designed and constructed a quadcopter from scratch as part of a group engineering project. I led the development of the embedded electronics and control software, and exercised my organisational skills in a very time-constrained environment.
  }

  % \rctline{Oct 2016}{
  %   Implemented a simple electronic stopwatch as an ASIC for a university design project. The design was then sent off to be manufactured. The project will resume later this year, when we will test the finished ICs.
  % }

  \rctline{Oct 2016}{
    Awarded the Zepler prize by the university, for obtaining the highest grade in first year out of all students on my course.
  }

  \rctline{Aug 2016}{
    Volunteered to help run the annual Computing and Microelectronics summer school at the university, where teams of 14--15 year olds completed a group engineering project while receiving support and mentoring from experts. Currently I am working on hardware manufacture and general planning for the next one, which will take place in August 2017.
  }

  % \rctline{Apr 2016}{
  %   Competed in the Inter-ACE cyber security competition as part of a team representing the university. The competition consisted of solving a variety of reverse engineering, binary exploitation and cryptography challenges in a race against the clock. We placed third out of ten teams.
  % }

  % \rctline{Jan 2016}{
  %   Built and tested a boost converter power supply for a design exercise as part of my degree course. The project involved running detailed simulations of the circuit, constructing the circuit on a protoboard, writing embedded control software in \texttt{C}, and testing and tuning the circuit to produce optimal results.
  % }

  \rctline{Aug 2015}{
    Began working on a hobby project to build a minimal working 8-bit processor out of discrete logic ICs, as inspired by a number of similar projects that I have come across online. Finding a balance between ease of implementation and ease of use has been a challenge and the processor has been redesigned a number of times because of this.
  }

  \rctline{Apr 2015}{
    Competed in the 2015 Student Robotics competition as part of a team of approximately eight people from my school, in which we were required to design and build an autonomous robot capable of playing a game of Capture the Flag. Despite having to overcome a number of challenges during the development of the robot, we managed to reach the semi-finals of the competition and place sixth out of fifty teams overall.
  }

  % \rctline{Mar 2014}{
  %   Completed a software system for planning meals for the week as part of my A-level Computing course. The task involved designing, implementing and testing a system for a real client.
  % }

  % \rctline{Jun 2013}{
  %   Developed a number of plugins for Minecraft, an online multiplayer game. They were written in Java and are now in use by dedicated game servers across the world.
  % }

  \rctline{Feb 2013}{
    Engaged in a week-long work experience placement at a local software company, \mbox{Pengower Ltd}. I assisted in the development and testing of their platform for business applications.
  }

  \rctline{Apr 2013}{
    Submitted my coursework for my GCSE Electronics qualification, which involved designing and constructing a small household burglar alarm system. I was responsible for the entire product design including devising the circuit and producing a custom printed circuit board.
  }

  \rctline{Aug 2012}{
    Participated in the Young Rewired State week-long hackathon, where we built a web application utilising open government data. My team and I came first in the \emph{Best Example of Coding} category and won a 3D printer, which we then spent a few months building.
  }

  % \rctline{Jul 2012}{
  %   Developed a software library for manipulating RDF, a structured format for open data. This project used the Go programming language, and its source code is available on Github.
  % }

  \rctline{Mar 2011}{
    Entered the national Pop Maths Quiz hosted by Sheffield Hallam University as part of a team from my school, placing first among roughly forty teams.
  }
\end{longtable}

\vspace{.2em}
